%Section: Work Experience at the top
\sectionTitle{Work Experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}

  \experience
    {Present}   {General Manager}{Wipro Consumer Care}{Bengaluru}
    {Sep 2021} {
Lead end-to-end strategy, brand stewardship, and P\&L management for Santoor—India’s iconic personal care brand.
                      \begin{itemize}
        \item {Spearheaded a \textbf{full portfolio relaunch} with product upgrade, packaging refresh, new variant and 360\textdegree {\link{https://www.youtube.com/watch?v=n19aGam0ZL0}{communication strategy}} to enhance youth relevance.}
        \item {Executed {\link{https://www.youtube.com/watch?v=n19aGam0ZL0&list=PLi9GkZhra4vXoOKk_liyoXTyBsThdhFqu}{multiple campaigns}} basis strong cultural insights deepening emotional resonance among consumers.}
        \item {Achieved sustained sales, market share growth reinforcing Santoor’s as India’s leading personal wash brand.}
        \item {Garnered \textbf{multiple industry awards} for excellence in brand building, innovation, and business performance.}
                      \end{itemize}
                  }
        {\textbf{Growth:}, Market Leadership} 
  \emptySeparator

  \experience
    {Sep 2021}   {Senior General Manager}{Emami Limited}{Mumbai}
    {Sep 2018} {
Directed P\&L and innovation strategy for Emami’s men’s grooming and legacy brands, leading a cross-functional team of eight.
                      \begin{itemize}
        \item {Initiated extensive qualitative, quantitative researches to landscape competition and consumer demand spaces in mens grooming market.}
        \item {\textbf{Repositioned} {\link{https://www.youtube.com/watch?v=wMstVMUB-gg&list=PLi9GkZhra4vVs6bQazNjfqnM_CUPvyooh}{Fair \& Handsome}} through data-led insighting, redefined target spaces, and built an \textbf{innovation roadmap} and launched a professional range aligned to leadership vision. }
        \item {Developed  \textbf{17 new products across 4 ranges} on HE within 12 months; 3 products ready ahead of schedule.}
        \item {Pioneered category-first {\link{https://www.youtube.com/watch?v=brENE9rYxtg&list=PLi9GkZhra4vXYLILTpr7BtHPLNAtJ3ObG}{dual fragrance packs}} driving \textbf{51\% sales growth} and \textbf{30 bps market share gain}.}
        \item {Reversed decline trends to deliver \textbf{54\% sequential growth} in H2 FY’21 amid pandemic constraints.}
                      \end{itemize}
                  }
        {\textbf{Transformation:}, P\&L, Category Creation} 
  \emptySeparator

  \experience
    {Aug 2018}     {Associate Director}{Escape Velocity} {Mumbai} 
    {Feb 2014}    {
Led end-to-end strategic engagements for CPG, consumer durables, education, and B2B clients, overseeing brand, growth, and marketing strategy managing a team of four.
                      \begin{itemize}
        \item {Delivered \textbf{12+ projects} spanning market entry, portfolio architecture, and go-to-market strategy.}
        \item {Presented to more than 50 different top executives on strategy approaches to solve business problems.}
        \item {Conducted eight capability-building workshops and mentored client marketing teams across sectors}
        \item {Acquired four new clients, contributing \textbf{30\% of firm’s revenue} over two years..}
        \item {Recognized for strategic inputs and actionable brand roadmaps adopted by client leadership teams.}                                                              
                      \end{itemize}
                    }
        {\textbf{Strategy:},Consulting, Training, Workshops} 
  \emptySeparator

  \experience
    {Jan 2014}     {Marketing Manager}{Colgate - Palmolive India Ltd.}{Mumbai}
    {Apr 2013}    {
Owned the P\&L across diverse portfolio of personal care (Palmolive, Halo, Charmis), home care (Axion), mouthwash (Plax), OTC (Pain Out), and Oral care (Sensitive Toothpaste) categories. 
                      \begin{itemize}
        \item {Launched three new product lines—Palmolive Ayurituel Shower Gels, Colgate Plax Visible White Mouthwash and Colgate Pain Out.}
        \item {Developed two new integrated communication campaigns on {\link{https://www.youtube.com/watch?v=NF1WfCP-P7E}{Pain Out}} and {\link{https://www.youtube.com/watch?v=-4PrmKVNNh8}{Sensitive Toothpaste}}.}
        \item {\textbf{Reversed volume decline} in  Plax Mouthwash, establishing a sustainable, growth-focused business model.}
                      \end{itemize}
                    }
        {\textbf{Innovation:},P\&L Management, IMC} 
  \emptySeparator

  \experience
    {Nov 2012}     {Group Product Manager}{Johnson \& Johnson Ltd.}{Mumbai}
    {May 2010}    {
Led strategy, innovation, and execution for Listerine Mouthwash. Helped rollout the brand strategy and communication roadmap for J\&J Consumer Products in Sri Lanka and Bangladesh.
                      \begin{itemize}
        \item {Shifted Listerine from OTC to consumer-focused positioning with localised manufacturing.} 
        \item {Launching two variants (Freshburst, {\link{https://www.youtube.com/watch?v=2_8xDJKu2_Q}{Cavity Fighter}}) capturing relevant benefit spaces and three 360\textdegree campaigns.}
        \item {Designed professional dental programs and launched the “{\link{https://www.youtube.com/watch?v=ZDUfiHt2bIE}{21-Day Challenge}}” trial \textbf{campaign adopted globally}.}
        \item {Delivered \textbf{83\% sales CAGR} and increased market share from 14\% to 30\%, making Listerine \#1 within 14 months.}
        \item {Supported Neutrogena’s e-commerce roll-out (2nd market worldwide) and onboarded the first social media agency for J\&J India.}
                      \end{itemize}
                    }
        {\textbf{Leadership:}, OTC Marketing, Professional Marketing, Social Media Marketing, eCommerce} 
  \emptySeparator

 \experience
  {May 2010}  {Group Key Account Manager (Dual Responsibility)}{Johnson \& Johnson Ltd.}{Mumbai}
  {Apr 2009}   {
Managed the Walmart account with responsibility for sales, profit targets, and in-store excellence
                      \begin{itemize}
        \item {Achieved \textbf{300\% overall sales growth} and \textbf{700\% comparable store growth} exceeding the Joint Business plans.}
        \item {Executed two first to market in India initiatives – an exclusive product pre-launch (mid-tier sanitary napkin) and a social sustainability initiative (clean water).}
                      \end{itemize}
                  }
        {\textbf{Execution:}, Key Account Management, JBP}
   \emptySeparator

 \experience
    {May 2010}  {Category Solutions Manager (Dual Responsibility)}{Johnson \& Johnson Ltd.}{Mumbai}
  {Apr 2008}   {
Managing baby, wound and OTC strategy for Modern Trade\textbf{ advising 17 key modern trade accounts} on category management. Led capability building and drove in-store excellence through shopper-centric strategies. 
                      \begin{itemize}
        \item {Served as the category captain for baby category in Walmart, partnering to design and execute category strategy, space planning and merchandising.}
        \item {Maintained \textbf{95\% share of Johnson's baby across chains}, positioning J\&J as the leader in baby category.}
        \item {Introduced MIS tools for tracking new product launch, promotional spends and ROI for spend optimisation.}
                      \end{itemize}
                  }
        { \textbf{Execution:}, Planogram, Merchandising, Spend Optimisation, ROI, Shopper Marketing}
  \emptySeparator

  \experience
  {Apr 2008}  {Product Manager}{Johnson \& Johnson Ltd.}{Mumbai}
  {Aug 2005}   {
Responsible for national product strategy for four Johnson’s Baby products (Powder, Gift Sets, Nappy Pads, and Buds) and all digital marketing initiatives for the Johnson's Baby brand. 
                      \begin{itemize}
        \item {Developed new growth strategy (adult leverage, {\link{https://www.youtube.com/watch?v=nqs6-_NWwzA}{emerging consumer}} and {\link{https://www.youtube.com/watch?v=Wfpkh6Vo7Tc}{low cost outlay}}) for Johnson's baby.}
         \item {Launched new Johnson's baby powder variants (Prickly heat, Milk Extracts). Revamped and relaunched gift sets.}
        \item {Delivered \textbf{17\% CAGR} over three years and 5\% market share gain on powder portfolio.}
        \item{Launched {\link{https://www.babycentre.in}{BabyCentre}}, J\&J’s digital parenting platform in India; Won internal Global Marketing Excellence Award.}
        \item {Implemented Sales Force Automation, CRM program for the Professional Marketing team.}
        \item {Onboarded the first digital media agency for J\&J.}
                      \end{itemize}
                  }
        {\textbf{Digitisation:}, NPD, SFA, CRM, Digital Marketing}
  \emptySeparator

  \experience
  {Aug 2005}  {Manager - Strategic Solutions Group}{Johnson \& Johnson Ltd.}{Mumbai}
  {Apr 2004}   {
Led the national sales operations excellence program to improve sales and supply chain processes, upgrade technology and enhance sales metrics for future growth.
                      \begin{itemize}
        \item {Designed and deployed Distributor Management System; integrating ERP with automated order management.}
        \item {Trained All India sales teams and 700+ distributors to drive adoption covering 80\% of sales managing a team of 15 in-field and 4 call-center executives.}
        \item {Received the J\&J IM excellence award for program execution.}
                      \end{itemize}
                  }
        {\textbf{Enablement:}, DMS,  VMR, ERP,  Sales MIS, Dashboards}
  \emptySeparator

  \experiencenotag
    {May 2004}  {Management Trainee}{Johnson \& Johnson Ltd.}{Mumbai}
  {May 2003}   {
                      \begin{itemize}
        \item {Sales: Delivered 17\% sales growth managing 16 distributors in Saurashtra, Gujarat.}
        \item {Marketing: Relaunched successful SKU in Johnson's baby contributing 15\% to annual sales.}
        \item {Operations - Planning: Automated capacity planning for operations, optimizing plant utilization.}
                              \end{itemize}
                  }
\end{experiences}
